Articles of Association of London Hackspace Ltd

### 2015-12-10 constitution/articles-body.tex
Clarify that a special resolution is required to remove a member.
Fixes #6

\item
  Membership is terminated if:
  \begin{enumerate}
  \item
    the member dies or, if it is an organisation, ceases to exist;
  \item
    the member resigns by written notice to the association unless, after
    the resignation, there would be fewer than three members;
  \item
    any sum due from the member to the association is not paid in full
    within two weeks of it falling due;
  \item
    the member is removed from membership by a resolution of the
    directors that it is in the best interests of the association that his
    or her or its membership is terminated. Such a resolution may only be
    passed after the Board has exhausted all other options under the
    Grievance Procedure.
\end{enumerate}

>>>>

\item
  Membership is terminated if:
  \begin{enumerate}
  \item
    the member dies or, if it is an organisation, ceases to exist;
  \item
    the member resigns by written notice to the association unless, after
    the resignation, there would be fewer than three members;
  \item
    any sum due from the member to the association is not paid in full
    within two weeks of it falling due;
  \item
    the member is removed from membership by a resolution of the
    directors that it is in the best interests of the association that his
    or her or its membership is terminated. Such a resolution may only be
    passed after the Board has exhausted all other options under the
    Grievance Procedure;
   \item
    a special resolution is passed stating that it is in the best interests
    of the association that his/her membership is terminated. Such a
    resolution may only be passed if the member has been given 14 days'
    notice of the resolution, and has been allowed to provide a statement
    to the general meeting.
   \end{enumerate}
